### 2021-06-14 README.rmd
Code coverage.

<!-- badges: start -->
[![](https://www.r-pkg.org/badges/version/listdown?color=blue)](https://cran.r-project.org/package=listdown)
[![R-CMD-check](https://github.com/kaneplusplus/listdown/workflows/R-CMD-check/badge.svg)](https://github.com/kaneplusplus/listdown/actions)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![](https://www.r-pkg.org/badges/version/listdown?color=blue)](https://cran.r-project.org/package=listdown)
[![R-CMD-check](https://github.com/kaneplusplus/listdown/workflows/R-CMD-check/badge.svg)](https://github.com/kaneplusplus/listdown/actions)
[![Codecov test coverage](https://codecov.io/gh/kaneplusplus/listdown/branch/master/graph/badge.svg)](https://codecov.io/gh/kaneplusplus/listdown?branch=master)
<!-- badges: end -->
